Non-kissing and non-crossing complexes \\ for locally gentle algebras

### 2018-07-04 draft/accordionComplexSurfaces.tex
Dissections are cellular and dual to each other.

It is not hard to see that~$\bar Q_{\dissection} = (Q_{\dissection}, I_{\dissection})$ is a locally gentle bound quiver,
and that the vertices corresponding to boundary edges of~$\dissection$ are blossoming vertices.
\pierreguy{Be more precise on the ``are blossiming vertices'' part of this sentence.}
\vincent{Explain also that we can get the blossoming quiver using the blossom points.}

@@

\subsection{The surface of a quiver}

>>>>

\begin{lemma}
\label{lemm:quiverOfDissectionIsLocallyGentle}
The bound quiver~$\bar Q_{\dissection} = (Q_{\dissection}, I_{\dissection})$ is a locally gentle bound quiver
\end{lemma}
\begin{proof}
Each arc~$a$ has two endpoints, and at each endpoint there is at most one arc coming immediately after~$a$ in the clockwise order, and at most one coming immediately before.
Thus, in~$Q_{\dissection}$, there are at most two arrows leaving~$a$ and at most two arriving in~$a$.
Among these arrows, those arising from the same endpoint of~$a$ will be composable, and those arising from different endpoints will yield relations.
Thus $\bar Q_{\dissection}$ is locally gentle.
\end{proof}

%Moreover, the vertices corresponding to boundary edges of~$\dissection$ are blossoming vertices.
%\pierreguy{Be more precise on the ``are blossiming vertices'' part of this sentence.}
\vincent{Explain also that we can get the blossoming quiver using the blossom points.}

@@

\subsection{The surface of a locally gentle bound quiver}
